---
title: "Assignment-B1"
author: "Irem YUCEL"
date: "01/11/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---


## Exercise 1: Make a function and Exercise 2: Document your Function

I used the below code snippet frequently, so I want to make this a function. The code does the following:
1) Takes a column from the data frame 
2) Removes the NA values
3) Counts the number of observations for each foctor of the column
4) Arranges in the descending order
5) Takes the top n categories with the most number of observations.

```{r}
library(tibble)
library(dplyr)
library(tidyr)
library(datateachr)

"""

data %>% 
  drop_na(x) %>%
  group_by(x) %>%
  summarise(c = n())%>%
  arrange(desc(c)) %>%
  top_n(n)
  
"""

#An example how the code works:
  
ex_data = tribble(
  ~x, ~y,  ~z,
  "a", 2,  3.6,
  "b", 1,  8.5,
  "a", 8,  8.5,
  "b", 1,  4.6,
  "c", 5,  3.7,
  "c", 1,  8.5,
  "c", 7,  8.5,
  "c", 4,  5.6,
  "c", 6,  8.5,
  "c", 7,  5.6,
  "b", 3,  8.5,
  "c", 1,  3.7,
  "b", 0,  8.5,
  "b", 1,  1.2,
)


test_snippet = ex_data %>% 
  drop_na(x) %>%
  group_by(x) %>%
  summarise(n = n())%>%
  arrange(desc(n)) %>%
  top_n(2)

print(test_snippet)

#Converting the snippet to a function

#' @title Column top n
#' 
#' Given a data and a column, this function counts the number of observations for each factor of the column levels and returns the top n with the most observations. If n is equal to the number of levels, then returns the number of observation for each level.

#' @param data is input data frame
#' @param column is a column of data to be used for counting
#' @param n is the number of top levels to return

#' @return a table with columns column(given as argument in function) and c (the count of observation) for each n (top) row

column_top_n <- function(data, col, n){
  data %>%
  drop_na({{col}}) %>%
  group_by({{col}}) %>%
  summarise(c = n())%>%
  arrange(desc(c)) %>%
  top_n(n)
}


```

## Exercise 3: Include examples

```{r}

column_top_n(ex_data, x, 2) #Example data I generated

column_top_n(vancouver_trees, genus_name, 3)#Vancouver trees data from datateachr package, returns the top 3 most common genus type

column_top_n(cancer_sample,diagnosis, 2) #Cancer sample data from datateachr package, in this case, the function is used to return the number of observations since there are 2 categories.

```

