---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# columnTopN

<!-- badges: start -->
<!-- badges: end -->

Given a data and a column, this function counts the number of observations for each factor of the column levels and returns the top n with the most observations. If n is equal to the number of levels, then returns the number of observation for each level.

## Installation

You can install the released version of columnTopN from [GitHub](https://github.com/) with:

``` {r}
library(devtools)
install_github("stat545ubc-2021/STAT545B-iremycl/columnTopN/")
```
## Example

This is a basic example using the Vancouver trees data from datateachr package. The function returns the top 3 most common genus type

```{r example}
library(columnTopN)
library(datateachr)
column_top_n(vancouver_trees, genus_name, 3)
```

